---
title: "Aides Drug"
author: "Erica Sanchez"
date: "October 30, 2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative AIDS drug is under test in clinical trials. Analyze the effectivenss if this drug across the board. Consdier population subgroups by gender, drug use, and sexual orientation. Finish this!  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

Methods used are catagorical variables; the graphic display is a bar chart,the numerical is a cross tabulation, and the influence is done in a chi sqrt. These variables are used to test the hypothesis that the aids drug abacavirinol is effective in treating people that contracted AIDS.

## Question 1: is the vaccine effective for the total population?

$H_0:$ preventative AIDS drug Abacavirinol is not effective in the general population.

$H_A$ perventative AIDS drug Abacavirinol is effective in the general population.

## Question 2: is the vaccine effective for the females?

$H_0:$ preventative AIDS drug Abacavirinol is not effective in the females.

$H_A$ perventative AIDS drug Abacavirinol is effective in the females.

## Question 3: is the vaccine effective for the males?

$H_0:$ preventative AIDS drug Abacavirinol is not effective in the males.

$H_A$ perventative AIDS drug Abacavirinol is effective in the males.

## Question 4: is the vaccine effective for the LGBTQ+?

$H_0:$ preventative AIDS drug Abacavirinol is not effective in the LGBTQ+.

$H_A$ perventative AIDS drug Abacavirinol is effective in the LGBTQ+.

## Question 5: is the vaccine effective for the drug users?

$H_0:$ preventative AIDS drug Abacavirinol is not effective in the drug users.

$H_A$ perventative AIDS drug Abacavirinol is effective in the drug users.

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
 
## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

## Total Population

```{r}
barchartGC(~infected+treatment, data=avast,type= 'percent', main="Total Population")
```

The barchart shows significant difference in the general population that took the drug verses the general population that took the placebo.  

## Females


```{r}
barchartGC(~infected+treatment, data= filter(avast, sex=="gal"), type= 'percent', main="Females")
```

The bar chart shows the effectiveness is related to gender, women are more susceptible.

## Males

```{r}
barchartGC(~infected+treatment, data= filter(avast, sex=="guy"), type= 'percent', main="Males")
```
The barchart shows significant difference in the males that took the drug verses the males that took the placebo.  

## LGBTQ+

```{r}
barchartGC(~infected+treatment, data= filter(avast, LGBTQ == "gay"), type= 'percent', main="LGBTQ")
```

The barchart shows significant difference in the LGBTQ that took the drug verses the LGBTQ that took the placebo. 

## Drug Users 

```{r}
barchartGC(~infected+treatment, data= filter(avast, DrugUser=="yes"), type= 'percent', main="Drug Users")
```

The barchart shows significant difference in the drug users that took the drug verses the drug users that took the placebo.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

Numerical summary is a cross tabulation.  

## Total Population

```{r}
tab1 = xtabs(~infected+treatment, data = filter(avast))
rowPerc(tab1)
```

the Numerical results show that within the none group for the total population of those not affected by aids, show that there is no difference between taking the actual drug or placebo.

## Females

gals = xtabs(~infected+treatment, data=avast)
rowPerc(gals)

```{r}
tab2 = xtabs(~infected+treatment, data = filter(avast,sex=="gal"))
rowPerc(tab2)
```

The female only population appears to show that the drug cut the percentage of those affected by aids in half.

## Males 

```{r}
tab3 = xtabs(~infected+treatment, data = filter(avast,sex=="guy"))
rowPerc(tab3)
```


The male only population appears to show a significant difference. That the drug seems to have some affect on contracting aids in the drug group.

## LGBTQ+

```{r}
tab4 = xtabs(~infected+treatment, data = filter(avast,LGBTQ=="gay"))
rowPerc(tab4)
```

The population of LGBTQ appears to show that the drug group has a larger affected rate than that of the placebo group. 

## Drug Users

```{r}
tab5 = xtabs(~infected+treatment, data = filter(avast,DrugUser=="yes"))
rowPerc(tab5)
```


The population of Drug Users appears to show that the group who were given the drug treatment amongst the aids group are at 1/4 of a difference from the total of aids infected from the placebo group.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(tab1)
```

The p value is 0. We reject the null hypothesis since the p<0.05, the hypothesis is that the effectiveness of the drug and the general population are related based the results of the chi-squared test of independence.


```{r}
chisqtestGC(tab2)
```

The p value is 0. We reject the null hypothesis since the p<0.05, the hypothesis is that the effectiveness of the drug and the females are related based the results of the chi-squared test of independence.

```{r}
chisqtestGC(tab3)
```

The p value is 1e-04. We reject the null hypothesis since the p<0.05, the hypothesis is that the effectiveness of the drug and the males are related based the results of the chi-squared test of independence.

```{r}
chisqtestGC(tab4)
```

The p value is 0. We reject the null hypothesis since the p<0.05, the hypothesis is that the effectiveness of the drug and the LGBTQ+ are related based the results of the chi-squared test of independence.

```{r}
chisqtestGC(tab5)
```

The p value is 0. We reject the null hypothesis since the p<0.05, the hypothesis is that the effectiveness of the drug and the Drug users are related based the results of the chi-squared test of independence.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

My results determine that there are different outcomes when taking the abacavirinol based off your gender, sexual orientation and if you are a drug user. If you are a female, you would not want to take abacavirinol, but if you are LGBTQ, then you would want to take it. If you are a drug user, you have a higher chance of getting aids if you take abacavirinol. The effectiveness of the AIDS drug Abacavirinol and gender are related.
